---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# HUD Brand Color palettes

This is a package forked from jkaupp/nord.
Adapted with Ministry of Housing and Urban Development (New Zealand) brand colours.


## Installation

You can install the current version of hud_palettes from github with:
(eventually, to be moved to hud-govt-nz)

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("saera-chun-hud/hud-palettes")
```

## The Palettes of `hud_palettes`

```{r palettes}
library(hud.palettes)
library(purrr)

par(mfrow=c(7, 2), lheight = 2, mar=rep(1, 4), adj = 0)

walk(names(hud_palettes), hud_show_palette)

```

## Example

This is a basic example which shows you how to use the different features in `hud_palettes`:

Here is how to use `scale_fill_hud()` with `ggplot2` 
```{r ggplot2_example}
library(ggplot2)
library(hud.palettes)

ggplot(diamonds) + 
  geom_bar(aes(x = cut, fill = clarity)) +
  scale_fill_hud("stronger")
```

Here is using the `hud_col` function, with built in colour-ramping, with the obligatory base r volcano.

```{r plot_example}
image(volcano, col = hud_col("rainbow", 20))
```

You can view the individual palettes in `hud_palettes` via `hud_show_palette()`

```{r show_palette}
hud_show_palette("kakariki")
```

## Acknowledgements

1. Full credit to Jake Kaupp (https://github.com/jkaupp/).
2. You can read HUD Brand Guidelines in Kete for more information on how to use HUD branding correctly.
3. Joe Winton's DRAFT D&P Power BI Dashboard standards (Can be found in Data & Products folder).

